Methods for Large Scale Learning to Rank

### 2014-09-25 report/Chapters/Background.tex
cross validation

\section{Cross-validation experiments}
\label{sec:cross_validation}
TODO

>>>>

\section{Cross-validation experiments}
\label{sec:cross_validation}
A cross-validation experiment \cite{kohavi1995}, sometimes called rotation estimation, is an experimental set-up for model evaluation where the data is split into $k$ chunks of approximately equal size, called \emph{folds}. One of the folds is used as validation set and one of the folds is used as test set, the rest of the $k-2$ folds are used as training data. This procedure is repeated $k$ times, such that each fold is once used for validation, once as test set, and $k-2$ times as training data. The performance can be measured in any model evaluation metric, and is averaged over the model performances on each of the folds. The goal of cross-validation is to define a data set to test the model in the training phase, in order to limit the problem of overfitting.\\

Cross-validation is one of the most frequently used model evaluations methods in the field of Machine Learning, including the Learning to Rank subfield. Often, folds in a cross-validation are created in a \emph{stratified} manner, meaning that the folds are created in such a way that the distributions of the target variable are approximately identical between the folds.
